An Open Repository of Real-Time COVID-19 Indicators

### 2021-09-30 indicators/code/indicator-paper-figures.Rmd
Mention data license
I haven't committed the data because it's quite large, but if we
deposit the code and data somewhere, it's good to know it's public
domain.
Improve description of Figure 6 (backfill)

```{r figure-6, message=FALSE, cache=TRUE}
SOURCES <- c("chng", "fb-survey", "jhu-csse", "jhu-csse")
SIGNALS <- c("smoothed_outpatient_cli", "smoothed_whh_cmnty_cli",
             "confirmed_incidence_prop", "deaths_incidence_prop")
NAMES <- c("lag", "CHNG-CLI", "CTIS-CLI-in-community", "Cases", "Deaths")

@@

pctile_df <- format_df(pctile_df)

pctile_df %>%
  ggplot(aes(x = lag, y = value, group = signal, color = signal)) +
  geom_line() +
  geom_text(data = filter(pctile_df, lag == min(lags)),
            aes(x = lag, y = value, label = signal, hjust = "left"),
            inherit.aes = FALSE, nudge_y = 0.015) +
  labs(x = "Days since initial issue",
       y = "95th percentile of absolute percent error",
       color = "Signal") +
  scale_y_continuous(labels = label_percent()) +
  scale_x_continuous(breaks = lags) +
  theme_bw() +
  theme(legend.position = "none")

@@

County-level vaccination data obtained [from the
CDC](https://data.cdc.gov/Vaccinations/COVID-19-Vaccinations-in-the-United-States-County/8xkx-amqh).
Data downloaded on August 2, 2021.

>>>>

```{r figure-6-data, message=FALSE, cache=TRUE}
SOURCES <- c("chng", "fb-survey", "jhu-csse", "jhu-csse")
SIGNALS <- c("smoothed_outpatient_cli", "smoothed_whh_cmnty_cli",
             "confirmed_incidence_prop", "deaths_incidence_prop")
NAMES <- c("lag", "CHNG-CLI", "CTIS-CLI-in-community", "Cases", "Deaths")

@@

pctile_df <- format_df(pctile_df)
```

```{r figure-6, cache=TRUE}
pctile_df %>%
  ggplot(aes(x = lag, y = value, group = signal, color = signal)) +
  geom_line() +
  geom_text(data = filter(pctile_df, lag == min(lags)),
            aes(x = lag, y = value, label = signal, hjust = "left"),
            inherit.aes = FALSE, nudge_y = 0.015) +
  labs(x = "Lag after events",
       y = "95th percentile of absolute percent error",
       color = "Signal") +
  scale_y_continuous(labels = label_percent()) +
  scale_x_continuous(breaks = lags) +
  theme_bw() +
  theme(legend.position = "none")

@@

County-level vaccination data obtained [from the
CDC](https://data.cdc.gov/Vaccinations/COVID-19-Vaccinations-in-the-United-States-County/8xkx-amqh).
Data downloaded on August 2, 2021. This data is in the public domain as a United
States government work.

### 2021-09-30 indicators/paper/paper.tex
Improve description of Figure 6 (backfill)

Claims-based signals typically undergo heavy backfill as additional claims are
processed and errors are corrected; the median relative error between initial
reports and final values is over 20\% for such data, and only after roughly 35
days do estimates typically match finalized values within 5\%. However, the
systematic nature of this backfill, as illustrated in Figure~\ref{fig:dv_as_of},
suggests that statistical models could be fit (potentially separately for each
location) to estimate the final values from preliminary reports. On the other
hand, official public health reporting of COVID cases and deaths can be subject
to revision as death certificates are audited and backlogs cleared, resulting in
thousands of cases and deaths being added or removed.
Figure~\ref{fig:backfill-compare} shows the amount of revision for several
signals, in terms of the 95th percentile of relative change between initial
estimates and revised estimates issued later; this shows that reported deaths
can have large revisions comparable to revisions in claims-based signals. This
backfill is much more difficult to predict, and thus claims data and other
sources may be a useful stand-in while public health reports are aggregated and
corrected.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/backfill-compare.pdf}
  \caption{95th percentile relative changes between initial values of key
    signals, compared to the final values reported much later. Calculated using
    each day's state-level estimates for the six months between October 15, 2020
    and April 15, 2021; final values were those reported 120 days after the end
    of this period. Even officially reported case and death data can have large
    revisions 30--60 days after initial reporting; much of this is driven by
    individual large revisions affecting specific states and dates, rather than
    systematic changes affecting all states and dates.}
  \label{fig:backfill-compare}
\end{figure}

>>>>

Claims-based signals typically undergo heavy backfill as additional claims are
processed and errors are corrected; the median relative error between initial
reports and final values is over 20\% for such data, and only after roughly 35
days do estimates typically match finalized values within 5\%. However, the
systematic nature of this backfill, as illustrated in Figure~\ref{fig:dv_as_of},
suggests that statistical models could be fit (potentially separately for each
location) to estimate the final values from preliminary reports. On the other
hand, official public health reporting of COVID cases and deaths can be subject
to revision as death certificates are audited and backlogs cleared, resulting in
thousands of cases and deaths being added or removed.
Figure~\ref{fig:backfill-compare} shows relative differences between early
signal values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can have large revisions comparable to
revisions in claims-based signals. This backfill is much more difficult to
predict, and thus claims data and other sources may be a useful stand-in while
public health reports are aggregated and corrected.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/backfill-compare.pdf}
  \caption{The 95th percentiles of relative changes between early reported
    values of key signals and final values reported much later. For each date
    between October 15, 2020 and April 15, 2021, the values for each state
    reported between 10 and 90 days later are compared to ``final'' versions
    recorded as of August 13, 2021, 120 days after April 15. Even officially
    reported case and death data can have large revisions 30--60 days or more
    after initial reporting; much of this is driven by individual large
    revisions affecting specific states and dates, rather than systematic
    changes affecting all states and dates.}
  \label{fig:backfill-compare}
\end{figure}
